Effects of Weather on Maize Yield in Kenya

### 2019-01-16 presentations/January2019/presentation4.tex
presentation first draft

@@

\note{Climate change has been increasing amplitudes and frequency of extreme weather events\\ Not every hazard turns into disaster\\
Relating NDMA Early warning classification to weather also various precip and weather indexes
r
b}

@@

\begin{itemize}
\item Narrowing the research question:
\begin{itemize}
\item Relationship of maize yield and weather in Kenya

\begin{itemize}
\item What is it about weather that causes drought related disasters?
\item Which particular characteristics of weather are the most 'responsible' for drought related disasters?
\end{itemize}
\end{itemize}
\end{itemize}

@@

>>>>

\begin{itemize}
\item Two predominant rainfall regimes in Kenya:

\begin{enumerate}
\item Arid and semi-Arid (ASAL): bi-modal
	\begin{itemize}
	\item MAM and OND
	\item \textcolor{red}{Short and Long rains}
	\end{itemize}
\item non-ASAL: uni-modal
	\begin{itemize}
	\item March to August
	\end{itemize}

\end{enumerate}
\item \textcolor{red}{Perhaps a map of ASAL and non-ASAL}

\end{itemize}
\end{frame}

\note{Climate change has been increasing amplitudes and frequency of extreme weather events\\ Not every hazard turns into disaster
r
b}

\begin{frame}\label{Intro-Approaches}
\frametitle{Intro-Approaches}

@@

\note{
Relating NDMA Early warning classification to weather also various precip and weather indexes
r
b}
%oooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooo
%oooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooooo

@@

\begin{itemize}
\item Narrowing the research question:
\begin{itemize}
\item Relationship of maize yield and weather in Kenya
\begin{itemize}
\item What is it about weather that causes drought related disasters?
\item Which particular characteristics of weather are the most 'responsible' for drought related disasters?
\end{itemize}
\end{itemize}
\end{itemize}

@@

\begin{frame}\label{Data}
\frametitle{Data}

\begin{itemize}
\item Maize yields
\begin{itemize}
\item source: Famine Early Warning Systems Network (FEWS NET)
\item County level, yearly, tonnes per hectare
\end{itemize}
\item Weather:
\begin{itemize}
\item Daily, $0.25^{\circ}$ resolution gridded data
\item Precipitation
	\begin{itemize}
	\item Climate Hazards Group InfraRed Precipitation with Station data (CHIRPS)
	\end{itemize}
\item Temperature
	\begin{itemize}
	\item Berkeley Earth
	\end{itemize}
	\item[$\blacksquare$] Aggregation needed to conform with the yield data
\end{itemize}

\note{After various problems with data (prices - not for every county, NDMA phases - not much of an objective criterion, probably political, various VCI values)
\\ so the decision about the approach was partially driven by data (un)availability \\ precip in mm, not sure if to put it into presentation as I would have to talk about units of temperature, mostly Kelvin but sometimes Celsius}
